Meta-analysis

### 2020-07-08 04_MetaAnalysis.Rmd
Finally have order and gaps working in forest plot

for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var){
   if(is.null(gap)){gap <- 0}

@@

            trows2 = c((stitle_row[1] - 2.5) - ord_rows[1:ks1[1]],
                       (stitle_row[2] - 2.5) - ord_rows[ks1[1]+1:ks1[2]],
                       (stitle_row[3] - 2.5) - ord_rows[ks1[2]+1:ks1[3]],
                       (stitle_row[4] - 2.5) - ord_rows[ks1[3]+1:ks1[4]],
                       (stitle_row[5] - 2.5) - ord_rows[ks1[4]+1:ks1[5]]
                       ),
            trows3 = ord_rows

              trows = c((stitle_row[1]-1.5):(stitle_row[1]-0.5 - ks1[1]),
                        (stitle_row[2]-1.5):(stitle_row[2]-0.5 - ks1[2]),
                        (stitle_row[3]-1.5):(stitle_row[3]-0.5 - ks1[3]),
                        (stitle_row[4]-1.5):(stitle_row[4]-0.5 - ks1[4]),
                        (stitle_row[5]-1.5):(stitle_row[5]-0.5 - ks1[5])))

@@

rows1 <- for_rows(156, ord_var = "spray_management")

@@

index1 <- dat1 %>%
   arrange(desc(spray_management), location, desc(grain_MD))%>%
   select(ID) %>%
   mutate(ID2 = order(ID))

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = (index1$ID2)+50,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5),
                slab = NA, 
                xlim = c(-3.5, 2.5),
                ylim = c(11,157),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.5,2,0.2))

>>>>

for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var, index){
   if(is.null(gap)){gap <- 0}

   trows_F <- function(x1, head_row, gap){
   if(x1 <= length(dat1$spray_management) &&
      x1 > length(dat1$spray_management) - (sum(dat1$spray_management == "Early"))){
      return(x1 + (head_row - length(dat1$spray_management)) - 2)}
   if(x1 <= length(dat1$spray_management) - (sum(dat1$spray_management == "Early")) &&
      x1 > length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late"))){
      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap))}
   if(x1 <= length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late"))&&
      x1 > length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
       sum(dat1$spray_management == "Recommended"))){
      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 2))}
   if(x1 <= length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
       sum(dat1$spray_management == "Recommended")) &&
      x1 > length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus"))){
      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 3))}
   if(x1 <= length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus")) &&
      x1 > length(dat1$spray_management) - 
      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus") +
       sum(dat1$spray_management == "Late_plus"))){
      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 4))}

@@

            trows2 = c((stitle_row[1] - 2.5) - ord_rows[1:ks1[1]],
                       (stitle_row[2] - 2.5) - ord_rows[ks1[1]+1:ks1[2]],
                       (stitle_row[3] - 2.5) - ord_rows[ks1[2]+1:ks1[3]],
                       (stitle_row[4] - 2.5) - ord_rows[ks1[3]+1:ks1[4]],
                       (stitle_row[5] - 2.5) - ord_rows[ks1[4]+1:ks1[5]]
                       ),

            trows3 = unlist(sapply(index1$ID2,trows_F, head_row = head_row, gap = gap)),

              trows = index)

@@

@@

index1 <- dat1 %>%
   mutate(spray_management = factor(spray_management, levels = c("Early", "Late","Recommended", "Recommended_plus","Late_plus")))%>%
   arrange(desc(spray_management), location, desc(grain_MD))%>%
   select(ID) %>%
   mutate(ID2 = order(ID))

rows1 <- for_rows(156, index = index1$ID2, gap = 5)

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = rows1$trows3,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5),
                slab = NA, 
                xlim = c(-3.5, 2.5),
                ylim = c(11,157),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.5,2,0.2))
